CA Affordabulity

### 2020-09-15 Untitled.Rmd
Update Untitled.Rmd

```{r rates pop,echo=FALSE, include=TRUE, message=FALSE,warning=FALSE, results='asis'}
rates <- read_csv("Data/affordability.csv")
priv <- select(b,PWSID,Ownership,D_POPULATI)
rates <- left_join(rates,b,by=c("pwsid"="PWSID")) 
rates <- rates[which(!is.na(rates$Ownership)),]
ggplot(rates, aes(x=log10(D_POPULATI), fill=Ownership)) +
  geom_density(alpha=0.4)
# Add mean lines

>>>>

```{r rates pop,echo=FALSE, include=TRUE, message=FALSE,warning=FALSE, results='asis'}
rates <- read_csv("Data/affordability.csv")
priv <- select(b,PWSID,Ownership,D_POPULATI)
rates <- left_join(rates,b,by=c("pwsid"="PWSID")) 
rates <- rates[which(!is.na(rates$Ownership)),]
ggplot(rates, aes(x=log10(D_POPULATI), fill=Ownership)) +
  geom_density(alpha=0.4)
# Add mean lines
ear13 <- read_tsv("Data/EAR/earsurveyresults_2013ry.zip",col_types="ccdcccdddc")
ear14 <- read_tsv("Data/EAR/earsurveyresults_2014ry.zip",col_types="ccdcccdddc")
ear15 <- read_tsv("Data/EAR/earsurveyresults_2015ry.zip",col_types="ccdcccdddc")
ear16 <- read_tsv("Data/EAR/earsurveyresults_2016ry.zip",col_types="ccdcccdddc")
ear17 <- read_tsv("Data/EAR/earsurveyresults_2017ry.zip",col_types="ccdcccdddc")
ear18 <- read_tsv("Data/EAR/earsurveyresults_2018ry.zip",col_types="ccdcccdddc")

ear <- bind_rows(ear13,ear14,ear15,ear16,ear17,ear18)
rm(ear13,ear14,ear15,ear16,ear17,ear18)
save(ear,file="Data/EAR/ear.rds")

hcf <- filter(ear,QuestionName=='WR 6 HCF DW Charges')
x <- filter(ear, QuestionName=='')
```
